### 2016-07-06 image_setup.tex
Most recent changes on image setup file
Image setup

\subsection{Loopback Device Setup}
After successfully resizing the image file, we use a loopback device to make
the Raspbian image available as a block device in the filesystem. For this
command to work, the tested administrator distribution must have the
\texttt{utils-linux} package with version 2.21 or higher. Otherwise, the
\texttt{-P} argument of \texttt{losetup} will appear as invalid.

@@

In general, the \ac{Raspi}s should be setup as similar as possible. However,
some particularities exist to differentiate the devices in principle. Also,
scripts containing further configurations for the \ac{Raspi}s are desirable
to be distributed as part of the common image. Therefore, here we present
the steps to setup basic properties of the \ac{Raspi}s and distributing
configuration scripts to each of them through the image.

Among the settings that may be different in the devices is their hostname.
The hostname helps the user to physically distinguish the devices from
each other. Thus, we require the devices in our testbed to have different
hostnames. Hence, we define the hostnames based on the \ac{MAC} addresses
of the \ac{Raspi}s wired Ethernet interface. Prior to this stage, the
\ac{MAC} address of a network card can be found using the command
\texttt{ifconfig} or \texttt{ip addr} on a given \ac{Raspi}.
We store the \ac{MAC} addresses and hostnames of the \ac{Raspi}s in the
configuration file \texttt{\${ROOTDIR}/home/pi/rasp\_config/nodes.csv} as
shown:

@@

We have packed the files and uploaded them to a webserver. These can be
retrieved with \texttt{wget} and unzipped into the Raspbian lite image:

% Get the files
\begin{lstlisting}[]
$ wget ${URL%/*}/rasp_config.zip
$ unzip rasp_config.zip -d ${ROOTDIR}/home/pi/
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

>>>>

\subsection{Loopback Device Setup}
After successfully resizing the image file, we use a loopback device to make
the Raspbian image available as a block device in the filesystem. For this
command to work, the tested administrator distribution must have the
\texttt{util-linux} package with version 2.21 or higher. Otherwise, the
\texttt{-P} argument of \texttt{losetup} will appear as invalid.

@@

In general, the \ac{Raspi}s should be setup as similar as possible. However,
some particularities exist to differentiate the devices in principle. Also,
scripts containing further configurations for the \ac{Raspi}s are desirable
to be distributed as part of the common image. Therefore, here we present
the steps to setup basic properties of the \ac{Raspi}s and distributing
configuration scripts to each of them through the image. First, we indicate
how to obtain and put our configuration scripts in the image. Later, we
describe the tasks performed by these configuration scripts. Nevertheless,
any testbed administrator might modify or include other tasks besides the
presented in this procedure according to his / her needs.

In our case, we have our configuration scripts are stored in a \texttt{.zip}
file located in a web server. We first retrieve this compressed file with
\texttt{wget} and unzip it locally into our Raspbian lite image. These
commands and the output of the last one are shown as follows:

% Get the configuration files that are compressed in a remote server
\begin{lstlisting}[]
$ wget ${URL%/*}/rasp_config.zip
$ unzip rasp_config.zip -d ${ROOTDIR}/home/pi/
Archive:  rasp_config.zip
   creating: ${ROOTDIR}/home/pi/rasp_config/
  inflating: ${ROOTDIR}/home/pi/rasp_config/nodes.csv
  inflating: ${ROOTDIR}/home/pi/rasp_config/set_hostname
  inflating: ${ROOTDIR}/home/pi/rasp_config/main
  inflating: ${ROOTDIR}/home/pi/rasp_config/update_rasp_config
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

Now,

Among the settings that we want to be different in the devices is
their hostname. The hostname helps the user to physically distinguish the
devices from each other. Thus, in our case we require the devices in our
testbed to have different hostnames. Moreover, besides this standard task,
other testbed administrators may need to also include other scripts to
configure their \ac{Raspi}s. Hence, we want to ensure that all the \ac{Raspi}
configuration scripts of any testbed administrators are obtained in a simple
way. Therefore, we ease this task by making the \ac{Raspi}s fetch the
configuration scripts during start up before running them.

Hence, we define the hostnames based on the \ac{MAC} addresses
of the \ac{Raspi}s wired Ethernet interface. Prior to this stage, the
\ac{MAC} address of a network card can be found using the command
\texttt{ifconfig} or \texttt{ip addr} on a given \ac{Raspi}.
We store the \ac{MAC} addresses and hostnames of the \ac{Raspi}s in the
configuration file \texttt{\${ROOTDIR}/home/pi/rasp\_config/nodes.csv} as
shown:

@@
